Mapping stellar surfaces\\ III: A Bayesian Approach to Doppler Imaging

### 2021-10-11 src/ms.tex
make spot ten percent

% TIMING RESULTS
\def\timeInferY{under 1 second\xspace}
\def\timeInferYB{about 5 seconds\xspace}
\def\timeInferYBS{about 30 seconds\xspace}
\def\timeInferYBSLOSNR{about 30 seconds\xspace}
\def\timeInferTwoSpec{about 20 minutes\xspace}

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.85\linewidth]{figures/spot_setup.pdf}
        \caption{%
            The basic setup for the \spot problem. 
            We compute the $l_\mathrm{max} = 15$ spherical harmonic expansion of a map where the word ``SPOT'' has been placed across the northern hemisphere (top left). 
            Each point on the surface is given the same spectrum, composed of a sum of synthetic Gaussian absorption lines (blue curve in the bottom panel).
            The specific intensity at each point on the surface is equal to this spectrum weighted by the intensity of the map, which is close to zero within the spot (point labeled \texttt{B}) and close to unity outside the spot (point labeled \texttt{A}).
            To generate the synthetic dataset (orange curves in the bottom panel), the star is inclined at $40^\circ$ with respect to the line of sight and the disk-integrated spectrum is computed at 16 equally-spaced phases between $-180^\circ$ and $180^\circ$, assuming an equatorial velocity $v = 60$ km/s (middle panel).
            The grey regions indicate wavelength regions outside the observation window, but whose features can still contribute to the observed spectrum due to rotational broadening.
        }
        \label{fig:spot_setup}
    \end{centering}
\end{figure}

>>>>

% TIMING RESULTS
\def\timeInferY{under 1 second\xspace}
\def\timeInferYB{about 1 second\xspace}
\def\timeInferYBS{about 30 seconds\xspace}
\def\timeInferYBSLOSNR{about 30 seconds\xspace}
\def\timeInferTwoSpec{about 20 minutes\xspace}

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.85\linewidth]{figures/spot_setup.pdf}
        \caption{%
            The basic setup for the \spot problem. 
            We compute the $l_\mathrm{max} = 15$ spherical harmonic expansion of a map where the word ``SPOT'' has been placed across the northern hemisphere (top left). 
            Each point on the surface is given the same spectrum, composed of a sum of synthetic Gaussian absorption lines (blue curve in the bottom panel).
            The specific intensity at each point on the surface is equal to this spectrum weighted by the intensity of the map, which is about ten percent within the spot (point labeled \texttt{B}) and close to unity outside the spot (point labeled \texttt{A}).
            To generate the synthetic dataset (orange curves in the bottom panel), the star is inclined at $40^\circ$ with respect to the line of sight and the disk-integrated spectrum is computed at 16 equally-spaced phases between $-180^\circ$ and $180^\circ$, assuming an equatorial velocity $v = 60$ km/s (middle panel).
            The grey regions indicate wavelength regions outside the observation window, but whose features can still contribute to the observed spectrum due to rotational broadening.
        }
        \label{fig:spot_setup}
    \end{centering}
\end{figure}
